Manuscript_physiological_consequences_blood_parasite_infection

### 2022-02-07 MS_physiology_infection.Rmd
Add files via upload

data2016_2020$Nest=as.factor(data2016_2020$Nest)
data2016_2020$Date=chron(as.character(data2016_2020$Date), format="d/m/y")
data2016_2020$Infection_intensity=as.factor(data2016_2020$Infection_intensity)
data2016_2020$Prevalence=as.factor(data2016_2020$Prevalence)
data2016_2020$Breathing_rate=scale(as.numeric(data2016_2020$Breathing_rate))
data2016_2020$Sex=as.factor(data2016_2020$Sex)
data2016_2020$Sampling_rank=as.factor(data2016_2020$Sampling_rank)
data2016_2020$Weight_g=as.numeric(data2016_2020$Weight.2)
data2016_2020$Wing_cm=as.numeric(data2016_2020$Wing)
data2016_2020$body_temperature=scale(as.numeric(data2016_2020$body_temperature))
data2016_2020$delta_body_condition=scale(as.numeric(data2016_2020$delta_body_condition))
data2016_2020$Ambient_Temperature_AvgC=as.numeric(data2016_2020$TemperatureAvgC)
data2016_2020$Treatment=as.factor(data2016_2020$Treatment)
data2016_2020$Year=as.factor(data2016_2020$Year)
data2016_2020$Growth_rate=scale(as.numeric(data2016_2020$Growth_rate))
data2016_2020$Growth_rate=scale(as.numeric(data2016_2020$Growth_rate_unlog))

@@

@@

treatment_meaninf_changes=ggplot(tab_mean)+
  aes(Timepoint,Mean_infection_intensity,group=Treatment)+
  geom_vline(xintercept = "Pre-treatment", linetype = "dashed", color='darkgrey')+
  geom_vline(xintercept = "Post-treatment", linetype = "dashed", color='darkgrey')+
  labs(y="Mean infection intensity")+
  ylim(c(0,3))+
  geom_line(aes(color=Treatment), size=2)+
  geom_errorbar(ymin=tab_mean$Mean_infection_intensity-tab_mean$se_inf_int, ymax=tab_mean$Mean_infection_intensity+tab_mean$se_inf_int,colour="black",
               size=1.5 , width=0.05)+
  stat_summary(fun=mean, colour="black", geom="point", 
               size=5)+ 
  scale_color_manual(values=c("lightgrey","black"))+
  theme_classic()+
  theme(axis.title.x = element_blank(), legend.text = element_text(size=16), legend.title = element_text(size=16), axis.title.y=element_text(size=18, margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=16), plot.margin = unit(c(0,0,0,30), "pt"))

@@

treatment_prevalence_changes+treatment_meaninf_changes+ plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

@@

gg1_pred=ggplot(mod_br)+
  aes(x,predicted)+
  geom_hline(yintercept = mean(mod_br$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Breathing rate")+
  ylim(c(min(mod_br$conf.low)-0.3,max(mod_br$conf.high)+0.5))+
  geom_errorbar(aes(ymin=mod_br$conf.low,ymax=mod_br$conf.high),colour="black",size=2, width=.1)+
  geom_errorbar(aes(ymin=mod_br$predicted-mod_br$std.error,ymax=mod_br$predicted+mod_br$std.error),size=8, colour=wes_palette("Zissou1",4), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=2, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
  aes(x=1, y=max(mod_br$conf.high)+0.3, xend=4, yend=max(mod_br$conf.high)+0.3))+
  geom_text(aes(x=2.5, y=max(mod_br$conf.high)+0.42),
  label="n.s.", size = 5)
```

@@

gg2_pred=ggplot(mod_bt)+
  aes(x,predicted)+
  geom_hline(yintercept = mean(mod_bt$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Body temperature")+
  geom_errorbar(aes(ymin=mod_bt$conf.low,ymax=mod_bt$conf.high),colour="black",size=2, width=.1)+
  geom_errorbar(aes(ymin=mod_bt$predicted-mod_bt$std.error,ymax=mod_bt$predicted+mod_bt$std.error),size=8,colour=wes_palette("Zissou1",4), width=0)+
  geom_point(color ="black", outlier.shape = NA, size=2, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title.y=element_text(size=14, margin=unit(c(0,3,0,0),"mm")),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=0.7, xend=4, yend=0.7))+
    geom_text(aes(x=2.5, y=0.78),
              label="n.s.", size = 5)

@@

lmer_bc=lmer(data= data2016_2020,delta_body_condition~Diff_Inf_Class+Diff_Inf_Class:Treatment+days_resample+Age_in_days+Year+(1|Nest))

@@

gg3_pred=ggplot(mod_bc)+
  aes(x,predicted)+
  geom_hline(yintercept = mean(mod_bc$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Δ Body condition")+
  geom_errorbar(aes(ymin=mod_bc$conf.low,ymax=mod_bc$conf.high),colour="black",size=2, width=.1)+
  geom_errorbar(aes(ymin=mod_bc$predicted-mod_bc$std.error,ymax=mod_bc$predicted+mod_bc$std.error),size=8,colour=wes_palette("Zissou1",4), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=2, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_bc$conf.high)+0.3, xend=4, yend=max(mod_bc$conf.high)+0.3))+
    geom_text(aes(x=2.5, y=max(mod_bc$conf.high)+0.4),
              label="n.s.", size = 5)

@@

gg4_pred=ggplot(mod_gr)+
  aes(x,predicted)+
  geom_hline(yintercept = mean(mod_gr$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Growth rate")+
  geom_errorbar(aes(ymin=mod_gr$conf.low,ymax=mod_gr$conf.high),colour="black",size=2, width=.1)+
  geom_errorbar(aes(ymin=mod_gr$predicted-mod_gr$std.error,ymax=mod_gr$predicted+mod_gr$std.error),size=8,colour=wes_palette("Zissou1",4), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=2, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title.y=element_text(size=14,margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 30, "pt"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_gr$conf.high)+0.2, xend=4, yend=max(mod_gr$conf.high)+0.2))+
    geom_text(aes(x=2.5, y=max(mod_gr$conf.high)+0.3),
              label="n.s.", size = 5)

@@

gg1_pred+gg2_pred+gg3_pred+gg4_pred + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

@@

mod_br_para <- mod_br_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m1)), levels=c(paste0(x,"\nn=",m1))))
mod_br_para$lower_CI=c(NA,mod_br_para$predicted[1]-0.44,mod_br_para$predicted[1]-0.86,mod_br_para$predicted[1]-0.57,mod_br_para$predicted[1]-0.58)
mod_br_para$higher_CI=c(NA,mod_br_para$predicted[1]+0.40,mod_br_para$predicted[1]+0.16,mod_br_para$predicted[1]+0.19,mod_br_para$predicted[1]+0.55)

gg1_pred_para=ggplot(mod_br_para)+
  aes(as.factor(mod_br_para$x),mod_br_para$predicted)+
  geom_hline(yintercept = mean(mod_br_para$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Breathing rate")+
  geom_errorbar(aes(ymin=mod_br_para$lower_CI,ymax=mod_br_para$higher_CI),colour="black",size=2, width=.1)+
  # geom_errorbar(aes(ymin=mod_br_para$predicted-mod_br_para$std.error,ymax=mod_br_para$predicted+mod_br_para$std.error),size=8,colour=wes_palette("Zissou1",5), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_br_para$higher_CI, na.rm=T)+0.2, xend=5, yend=max(mod_br_para$higher_CI, na.rm=T)+0.2))+
    geom_text(aes(x=3, y=max(mod_br_para$higher_CI, na.rm=T)+0.27),
              label="n.s.", size = 5)
```

@@

mod_bt_para <- mod_bt_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m2)), levels=c(paste0(x,"\nn=",m2))))
mod_bt_para$lower_CI=c(NA,mod_bt_para$predicted[1]-0.44,mod_bt_para$predicted[1]-0.72,mod_bt_para$predicted[1]-0.69,mod_bt_para$predicted[1]-1.45)
mod_bt_para$higher_CI=c(NA,mod_bt_para$predicted[1]+0.56,mod_bt_para$predicted[1]+0.29,mod_bt_para$predicted[1]+0.22,mod_bt_para$predicted[1]+(-0.23))

@@

lmer_bc_para=lmer(data= data2016_2020,delta_body_condition~Infection_intensity+Infection_intensity:Treatment+days_resample+Age_in_days+Year+(1|Nest))

@@

mod_bc_para <- mod_bc_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m3)), levels=c(paste0(x,"\nn=",m3))))
mod_bc_para$lower_CI=c(NA,mod_bc_para$predicted[1]-0.04,mod_bc_para$predicted[1]-0.72,mod_bc_para$predicted[1]-0.53,mod_bc_para$predicted[1]-1.02)
mod_bc_para$higher_CI=c(NA,mod_bc_para$predicted[1]+0.76,mod_bc_para$predicted[1]+0.26,mod_bc_para$predicted[1]+0.22,mod_bc_para$predicted[1]+(-0.05))

gg3_pred_para=ggplot(mod_bc_para)+
  aes(as.factor(mod_bc_para$x),mod_bc_para$predicted)+
  geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Δ Body condition")+
  geom_errorbar(aes(ymin=mod_bc_para$lower_CI,ymax=mod_bc_para$higher_CI),colour="black",size=2, width=.1)+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=-0.325843-1.6, xend=5, yend=-0.325843-1.6))+
    geom_text(aes(x=3, y=-0.325843-1.75),
              label="p=0.07", size = 5)+
  geom_segment(size = .8,
                 aes(x=1, y=-0.325843-1.45, xend=1, yend=-0.325843-1.6))+
  geom_segment(size = .8,
                 aes(x=5, y=-0.325843-1.6, xend=5, yend=-0.325843-1.45))

@@

mod_gr_para <- mod_gr_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m4)), levels=c(paste0(x,"\nn=",m4))))
mod_gr_para$lower_CI=c(NA,mod_gr_para$predicted[1]-0.11,mod_gr_para$predicted[1]-0.79,mod_gr_para$predicted[1]-0.54,mod_gr_para$predicted[1]-0.89)
mod_gr_para$higher_CI=c(NA,mod_gr_para$predicted[1]+0.58,mod_gr_para$predicted[1]+0.06,mod_gr_para$predicted[1]+0.10,mod_gr_para$predicted[1]+0.04)

gg4_pred_para=ggplot(mod_gr_para)+
  aes(as.factor(mod_gr_para$x),mod_gr_para$predicted)+
  geom_hline(yintercept = mean(mod_gr_para$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Growth rate")+
  geom_errorbar(aes(ymin=mod_gr_para$lower_CI,ymax=mod_gr_para$higher_CI),colour="black",size=2, width=.1)+
  # geom_errorbar(aes(ymin=mod_gr_para$predicted-mod_gr_para$std.error,ymax=mod_gr_para$predicted+mod_gr_para$std.error),size=8,colour=wes_palette("Zissou1",5), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=mod_gr_para$predicted[1]-0.79-0.5, xend=5, yend=mod_gr_para$predicted[1]-0.79-0.5))+
    geom_text(aes(x=3, y=mod_gr_para$predicted[1]-0.79-0.63),
              label="p=0.09", size = 5)+
  geom_segment(size = .8,
                 aes(x=1, y=mod_gr_para$predicted[1]-0.79-0.35, xend=1, yend=mod_gr_para$predicted[1]-0.79-0.5))+
  geom_segment(size = .8,
                 aes(x=5, y=mod_gr_para$predicted[1]-0.79-0.5, xend=5, yend=mod_gr_para$predicted[1]-0.79-0.3))

@@

gg1_pred_para+gg2_pred_para+gg3_pred_para+gg4_pred_para + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

@@

# First sampling parasitemia

## Same with delta body condition

tol_resdata$Infection_intensity.1=as.numeric(tol_resdata$Infection_intensity.1)
tolres_deltamod=lm(delta_body_condition~Infection_intensity.1*Diff_Inf_Class, data=tol_resdata)

# comparison of slopes among infection stages

lms_delta=lstrends(tolres_deltamod,~Diff_Inf_Class:Infection_intensity.1, var="Infection_intensity.1")

# comparison of slopes to zero

# body condition change - first infection intensity

tolres_delta_first=ggplot(data =data2016_2020[! data2016_2020$Infection_intensity.1 %in% NA & ! data2016_2020$Diff_Inf_Class %in% c(NA,"Uninfected"),], aes(y=delta_body_condition,x=as.numeric(Infection_intensity.1),col=Diff_Inf_Class))+
    geom_jitter(size=3, alpha=0.5)+
    geom_smooth(alpha=0.2, size=1.5, method='lm',se = T)+
    labs(title = "First sampling", y="Body condition change",x="Parasitemia \n at first sampling", col='Infection stages')+
    # scale_x_continuous(breaks=seq(1,5,1),labels=c("0","1","2","3","4"))+
    scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00"))+
    theme_classic()+
    theme(legend.position = "none", axis.text = element_text(size=16), axis.title = element_text(size=18))

@@

tolres_deltamod=lm(delta_body_condition~Infection_intensity*Diff_Inf_Class, data=tol_resdata)

@@

## plot

tolre_sum=tolre_sum[!tolre_sum$Diff_Inf_Class %in% "Uninfected",]

>>>>

data2016_2020$Nest=as.factor(data2016_2020$Nest)
data2016_2020$Date=chron(as.character(data2016_2020$Date), format="d/m/y")
data2016_2020$Infection_intensity=as.factor(data2016_2020$Infection_intensity)
data2016_2020$Prevalence=as.factor(data2016_2020$Prevalence)
data2016_2020$Breathing_rate=as.numeric(data2016_2020$Breathing_rate)
data2016_2020$Sex=as.factor(data2016_2020$Sex)
data2016_2020$Sampling_rank=as.factor(data2016_2020$Sampling_rank)
data2016_2020$Weight_g=scale(as.numeric(data2016_2020$Weight.2))
data2016_2020$Wing_cm=as.numeric(data2016_2020$Wing)
data2016_2020$body_temperature=as.numeric(data2016_2020$body_temperature)
data2016_2020$delta_body_condition=as.numeric(data2016_2020$delta_body_condition)
data2016_2020$Ambient_Temperature_AvgC=scale(as.numeric(data2016_2020$TemperatureAvgC))
data2016_2020$Treatment=as.factor(data2016_2020$Treatment)
data2016_2020$Year=as.factor(data2016_2020$Year)
data2016_2020$Growth_rate=as.numeric(data2016_2020$Growth_rate_unlog)
data2016_2020$days_resample=scale(data2016_2020$days_resample)
data2016_2020$Age_in_days=scale(as.numeric(data2016_2020$Age_in_days))

@@

mean_infint=data.frame(Sampling_rank=factor(c(rep("1",length(data2016_2020$Sampling_rank)),as.character(data2016_2020$Sampling_rank)),levels=c("1","2"), labels = c("Pre-treatment","Post-treatment")),Infection_intensity=as.numeric(c(as.character(data2016_2020$Infection_intensity.1),as.character(data2016_2020$Infection_intensity))),Treatment=factor(c(as.character(rep(data2016_2020$Treatment,2))),levels = c("Control","Malarone")))

@@

treatment_meaninf_changes=ggplot(mean_infint)+
  aes(Sampling_rank,Infection_intensity,group=Treatment, fill=Treatment)+
  geom_vline(xintercept = "Pre-treatment", linetype = "dashed", color='darkgrey')+
  geom_vline(xintercept = "Post-treatment", linetype = "dashed", color='darkgrey')+
  labs(y="Mean infection intensity")+
  # ylim(c(0,3))+
  geom_point(aes(colour=Treatment),position=position_jitterdodge(jitter.width = 0.2, jitter.height = 0.5))+  # position=position_jitterdodge()
  # geom_line(aes(group=Treatment,color=Treatment, fill=Treatment),size=2)+
  stat_summary(fun=mean, geom="line",size=2,color=c("lightgrey","black","black","lightgrey"))+
  stat_summary(fun=mean, geom="point",size=5)+
  stat_summary(geom="errorbar", width=0.04, size=2)+
  scale_color_manual(values=c("lightgrey","black"))+
  theme_classic()+
  theme(axis.title.x = element_blank(), legend.text = element_text(size=16), legend.title = element_text(size=16), axis.title.y=element_text(size=18, margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=16), plot.margin = unit(c(0,0,0,30), "pt"))

@@

Fig2=treatment_prevalence_changes+treatment_meaninf_changes+ plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

ggsave(Fig2,filename = "./Figs/efficiency_malarone.png",units = "px", width = 6000, height = 3000)

@@

gg1_pred=ggplot(mod_br)+
  aes(x,predicted)+
  geom_hline(yintercept = mean(mod_br$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Breathing rate")+
  ylim(c(min(mod_br$conf.low)-1.5,max(mod_br$conf.high)+1.5))+
  geom_errorbar(aes(ymin=mod_br$conf.low,ymax=mod_br$conf.high),colour="black",size=2, width=.1)+
  geom_errorbar(aes(ymin=mod_br$predicted-mod_br$std.error,ymax=mod_br$predicted+mod_br$std.error),size=8, colour=wes_palette("Zissou1",4), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=2, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
  aes(x=1, y=max(mod_br$conf.high)+1, xend=4, yend=max(mod_br$conf.high)+1))+
  geom_text(aes(x=2.5, y=max(mod_br$conf.high)+1.5),
  label="n.s.", size = 5)
```

@@

gg2_pred=ggplot(mod_bt)+
  aes(x,predicted)+
  geom_hline(yintercept = mean(mod_bt$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Body temperature")+
  geom_errorbar(aes(ymin=mod_bt$conf.low,ymax=mod_bt$conf.high),colour="black",size=2, width=.1)+
  geom_errorbar(aes(ymin=mod_bt$predicted-mod_bt$std.error,ymax=mod_bt$predicted+mod_bt$std.error),size=8,colour=wes_palette("Zissou1",4), width=0)+
  geom_point(color ="black", outlier.shape = NA, size=2, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title.y=element_text(size=14, margin=unit(c(0,3,0,0),"mm")),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=40.6, xend=4, yend=40.6))+
    geom_text(aes(x=2.5, y=40.7),
              label="n.s.", size = 5)

@@

lmer_bc=lmer(data= data2016_2020,delta_body_condition~Diff_Inf_Class+Diff_Inf_Class:Treatment+days_resample+Age_in_days+Sex+Year+(1|Nest))

@@

gg3_pred=ggplot(mod_bc)+
  aes(x,predicted)+
  geom_hline(yintercept = mean(mod_bc$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Δ Body condition")+
  geom_errorbar(aes(ymin=mod_bc$conf.low,ymax=mod_bc$conf.high),colour="black",size=2, width=.1)+
  geom_errorbar(aes(ymin=mod_bc$predicted-mod_bc$std.error,ymax=mod_bc$predicted+mod_bc$std.error),size=8,colour=wes_palette("Zissou1",4), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=2, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_bc$conf.high)+17, xend=4, yend=max(mod_bc$conf.high)+17))+
    geom_text(aes(x=2.5, y=max(mod_bc$conf.high)+23),
              label="n.s.", size = 5)

@@

gg4_pred=ggplot(mod_gr)+
  aes(x,predicted)+
  geom_hline(yintercept = mean(mod_gr$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Growth rate")+
  geom_errorbar(aes(ymin=mod_gr$conf.low,ymax=mod_gr$conf.high),colour="black",size=2, width=.1)+
  geom_errorbar(aes(ymin=mod_gr$predicted-mod_gr$std.error,ymax=mod_gr$predicted+mod_gr$std.error),size=8,colour=wes_palette("Zissou1",4), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=2, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title.y=element_text(size=14,margin= unit(c(0, 3, 0, 0), "mm")),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 30, "pt"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_gr$conf.high)+1.2, xend=4, yend=max(mod_gr$conf.high)+1.2))+
    geom_text(aes(x=2.5, y=max(mod_gr$conf.high)+2),
              label="n.s.", size = 5)

@@

fig4=gg1_pred+gg2_pred+gg3_pred+gg4_pred + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

ggsave(fig4,filename = "./Figs/predicted_physio_param_infection_stages.png",units = "px", width = 3700, height = 3700)

@@

mod_br_para <- mod_br_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m1)), levels=c(paste0(x,"\nn=",m1))))
mod_br_para$lower_CI=c(31.11, mod_br_para$predicted[1]-2.96, mod_br_para$predicted[1]-6.49,mod_br_para$predicted[1]-4.67, mod_br_para$predicted[1]-4.63)
mod_br_para$higher_CI=c(41.42,mod_br_para$predicted[1]+3.90,mod_br_para$predicted[1]+1.75,mod_br_para$predicted[1]+1.46,mod_br_para$predicted[1]+4.45)

gg1_pred_para=ggplot(mod_br_para)+
  aes(as.factor(mod_br_para$x),mod_br_para$predicted)+
  geom_hline(yintercept = mean(mod_br_para$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Breathing rate")+
  geom_errorbar(aes(ymin=mod_br_para$lower_CI,ymax=mod_br_para$higher_CI),colour="black",size=2, width=.1)+
  # geom_errorbar(aes(ymin=mod_br_para$predicted-mod_br_para$std.error,ymax=mod_br_para$predicted+mod_br_para$std.error),size=8,colour=wes_palette("Zissou1",5), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=max(mod_br_para$higher_CI, na.rm=T)+1.2, xend=5, yend=max(mod_br_para$higher_CI, na.rm=T)+1.2))+
    geom_text(aes(x=3, y=max(mod_br_para$higher_CI, na.rm=T)+2),
              label="n.s.", size = 5)
```

@@

mod_bt_para <- mod_bt_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m2)), levels=c(paste0(x,"\nn=",m2))))
mod_bt_para$lower_CI=c(39.40,mod_bt_para$predicted[1]-0.40,mod_bt_para$predicted[1]-0.60,mod_bt_para$predicted[1]-0.65,mod_bt_para$predicted[1]-1.38)
mod_bt_para$higher_CI=c(40.40,mod_bt_para$predicted[1]+0.55,mod_bt_para$predicted[1]+0.36,mod_bt_para$predicted[1]+0.19,mod_bt_para$predicted[1]+(-0.24))

@@

lmer_bc_para=lmer(data= data2016_2020,delta_body_condition~Infection_intensity+Infection_intensity:Treatment+days_resample+Age_in_days+Sex+Year+(1|Nest))

@@

mod_bc_para <- mod_bc_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m3)), levels=c(paste0(x,"\nn=",m3))))
mod_bc_para$lower_CI=c(-65.99,mod_bc_para$predicted[1]-5.71,mod_bc_para$predicted[1]-53.27,mod_bc_para$predicted[1]-37.05,mod_bc_para$predicted[1]-71.88)
mod_bc_para$higher_CI=c(25.59,mod_bc_para$predicted[1]+51.67,mod_bc_para$predicted[1]+16.43,mod_bc_para$predicted[1]+16.17,mod_bc_para$predicted[1]+4.09)

gg3_pred_para=ggplot(mod_bc_para)+
  aes(as.factor(mod_bc_para$x),mod_bc_para$predicted)+
  geom_hline(yintercept = mean(mod_bc_para$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Δ Body condition")+
  geom_errorbar(aes(ymin=mod_bc_para$lower_CI,ymax=mod_bc_para$higher_CI),colour="black",size=2, width=.1)+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=-105, xend=5, yend=-105))+
    geom_text(aes(x=3, y=-110),
              label="p=0.08", size = 5)+
  geom_segment(size = .8,
                 aes(x=1, y=-105, xend=1, yend=-105+5))+
  geom_segment(size = .8,
                 aes(x=5, y=-105, xend=5, yend=-105+5))

@@

mod_gr_para <- mod_gr_para %>% 
  mutate(x = factor(c(paste0(x,"\nn=",m4)), levels=c(paste0(x,"\nn=",m4))))
mod_gr_para$lower_CI=c(11.44,mod_gr_para$predicted[1]-2.22,mod_gr_para$predicted[1]-10.47,mod_gr_para$predicted[1]-6.60,mod_gr_para$predicted[1]-11.39)
mod_gr_para$higher_CI=c(25.14,mod_gr_para$predicted[1]+7.08,mod_gr_para$predicted[1]+0.92,mod_gr_para$predicted[1]+1.91,mod_gr_para$predicted[1]+0.89)

gg4_pred_para=ggplot(mod_gr_para)+
  aes(as.factor(mod_gr_para$x),mod_gr_para$predicted)+
  geom_hline(yintercept = mean(mod_gr_para$predicted, na.rm=T), linetype = "dashed")+
  labs(x="", y="Growth rate")+
  geom_errorbar(aes(ymin=mod_gr_para$lower_CI,ymax=mod_gr_para$higher_CI),colour="black",size=2, width=.1)+
  # geom_errorbar(aes(ymin=mod_gr_para$predicted-mod_gr_para$std.error,ymax=mod_gr_para$predicted+mod_gr_para$std.error),size=8,colour=wes_palette("Zissou1",5), width=0,)+
  geom_point(color ="black", outlier.shape = NA, size=4, width=.3)+
  theme_classic()+
  theme(legend.position="none", axis.title=element_text(size=14),  axis.text=element_text(size=12), axis.line.x = element_blank(), axis.ticks.x = element_blank(), plot.margin = margin(0, 0, 0, 0, "cm"), plot.title = element_text(hjust = 0.5, face="bold"))+
  geom_segment(size = .8,
                 aes(x=1, y=5, xend=5, yend=5))+
    geom_text(aes(x=3, y=5-0.63),
              label="p=0.09", size = 5)+
  geom_segment(size = .8,
                 aes(x=1, y=5, xend=1, yend=5+0.5))+
  geom_segment(size = .8,
                 aes(x=5, y=5, xend=5, yend=5+0.5))

@@

fig5=gg1_pred_para+gg2_pred_para+gg3_pred_para+gg4_pred_para + plot_annotation(tag_levels = 'A')& 
  theme(plot.tag = element_text(size = 16, face = "bold"))

ggsave(fig5,filename = "./Figs/predicted_physio_param_infection_intensities.png",units = "px", width = 3700, height = 3700)

@@

# # First sampling parasitemia
# 
# ## Same with delta body condition
# 
# tol_resdata$Infection_intensity.1=as.numeric(tol_resdata$Infection_intensity.1)
# tolres_deltamod=lm(body_condition.1~Infection_intensity.1*Diff_Inf_Class, data=tol_resdata)
# 
# # comparison of slopes among infection stages 
# 
# lms_delta=lstrends(tolres_deltamod,~Diff_Inf_Class:Infection_intensity.1, var="Infection_intensity.1")
# 
# contrast(lms_delta,"pairwise")
# 
# tolre_deltasum=summary(lms_delta)
# 
# # comparison of slopes to zero
# 
# summary(lms_delta, infer=T)
# 
# # body condition change - first infection intensity
# 
# tolres_delta_first=ggplot(data =data2016_2020[! data2016_2020$Infection_intensity.1 %in% NA & ! data2016_2020$Diff_Inf_Class %in% c(NA,"Uninfected"),], aes(y=body_condition.1,x=as.numeric(Infection_intensity.1),col=Diff_Inf_Class))+
#     geom_jitter(size=3, alpha=0.5)+
#     geom_smooth(alpha=0.2, size=1.5, method='lm',se = T)+
#     labs(title = "First sampling", y="Body condition change",x="Parasitemia \n at first sampling", col='Infection stages')+
#     # scale_x_continuous(breaks=seq(1,5,1),labels=c("0","1","2","3","4"))+
#     scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00"))+
#     theme_classic()+
#     theme(legend.position = "none", axis.text = element_text(size=16), axis.title = element_text(size=18))

@@

tolres_deltamod=lm(body_condition.2~Infection_intensity*Diff_Inf_Class, data=tol_resdata)

@@

# ## plot
# 
# tolres=ggplot(data =data2016_2020[! data2016_2020$Infection_intensity %in% c(NA,0) & ! data2016_2020$Diff_Inf_Class %in% NA,], aes(y=body_condition.2,x=as.numeric(Infection_intensity),col=Diff_Inf_Class))+
#   geom_jitter(size=3, alpha=0.5)+
#   geom_smooth(alpha=0.2, size=1.5, method='lm',se = T)+
#   labs(y="Body condition \n at second sampling",x="Parasitemia \n at second sampling", col='Infection stages')+
#   scale_x_continuous(breaks=seq(2,5,1),labels=c("1","2","3","4"))+
#   scale_color_manual(labels = c("Increasing", "Peak", "Decreasing"),values = c("#3B9AB2", "#E1AF00", "#F21A00"))+
#   theme_classic()+
#   theme(legend.text = element_text(size=19),legend.title = element_text(size=22), axis.text = element_text(size=16), axis.title = element_text(size=18))
